Finite Property Convex Elicitation Paper

### 2019-01-22 jessie-writeup/jw-holes-clarified.tex
Updated writeup and simplified proofs slightly

\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$''}
\end{notation}
\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}

@@

We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
\jessiet{Do we want the above statement?}

@@

\begin{definition}
A property $\Gamma: \P \to \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ so that $\Gamma_r = \Gamma_{r'}$. 
	\jessie{Double check/clarify the statement of $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	Therefore, we know that $\gamma(p) = [r]$ for all $p\in \P$.
	Since $[r]$ is well-defined for every report $r \in \R$, we know $\gamma$ is nondegenerate.
	(This can also be seen by the closure of level sets that union to the simplex.)

@@

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there are reports $r, r' \in \R'$ so that $r \neq r'$ and $\gamma_{r'} \subsetneq \gamma_{r}$.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (once we reduce to equivalence classes-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere, but for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. 
	As the redundancy of $\gamma$ contradicts the elicitability of $\gamma$, so we conclude $\gamma$ is nonredundant.

@@

	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

@@

\begin{proof}
	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
	We want to show $\strip(\gamma) = \strip(\Gamma')$.
	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.
	Therefore, there is a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$\footnote{Abusing notation for set $X$, $\varphi(X) = \{ \varphi(x) : x\in X \}$  } for all $p \in \P$.
	Therefore, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
\end{proof}

\begin{conjecture}\label{conj:trim-full-dim}
	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
\end{conjecture}

\begin{proof}[Proof Sketch]
	\jessie{Uses: Conjecture~\ref{conj:gam-prime-exists}.}

	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional.

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the property $\Gamma: \P \toto \reals^d$ be convex elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R$ so that $\gamma \preceq \Gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
	%\jessie{Statement needs to be changed so instead of assuming embedding, just want $\gamma \preceq \Gamma$.}
\end{conjecture}

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	For $\theta \in \strip(\Gamma)$, there is some report $r \in \reals^d$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
	Now consider the report $r' = [r]$.
	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
	Therefore, there is some $r' \in \R$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
%	
%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
\end{proof}

@@

  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
  \item $\trim(\Gamma)$ is finite. \jessie{IMO, we can cut given the next point}
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}

@@

\item[$4 \implies 1$] 
Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Conjecture~\ref{conj:gam-prime-exists}.
Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
Since $\trim(\Gamma)$ is finite, we then know $\R'$ is finite, and so $\gamma$ is a finite property.
We can then easily see that $r \in \gamma(r) \implies r \in \Gamma(p)$ as $\R' \subseteq \reals^d$.
Additionally, for any $r \in \R'$ so that $r \in \Gamma(p)$, we know that $r \in \Gamma|_{\R'} = \gamma$.
Therefore, $\Gamma$ embeds $\Gamma|_{\R'} = \gamma$.

%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
%First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).

@@

\item [$1 \implies 5$]
We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item [$5 \implies 2$]
Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.

\item [$2 \implies 3$]
	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Conjecture~\ref{conj:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}

@@

\item [$3 \implies 4$]
Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.

\item[$2 \implies 1$]
\jessie{Only needed if we decide to cut 3 and 4.}
$\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists} is an embedding of $\Gamma$.
\end{enumerate}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
\end{definition}

@@

\begin{conjecture}
A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
\end{conjecture}
\begin{proof}

\begin{enumerate}
\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
\item[$\impliedby$] A convex set of positive measure contains the ball, which is a superset of a convex hull of affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
\end{enumerate}
\end{proof}

>>>>

\jessie{Is there a better way to say this? ex: ``For all $r' \in \R'$, there is an $r\in \R$ such that $\Gamma_r = \gamma_{r'}$'' ... this suggests the properties are equivalent-ish.}
\end{notation}
\jessie{In the latter definition, if $\Gamma$ embeds $\gamma$, then $\gamma \preceq \Gamma$ since $\Gamma_{\varphi(r')} = \gamma_{r'}$ for all $r' \in \R'$.}

@@

We slightly abuse notation to say that if $\Gamma$ is an embedding of $\gamma$, then $\gamma \preceq \Gamma$ if and only if $\varphi(\gamma(p)) = \Gamma(p) \cap \varphi(\R')$\footnote{If $S$ is a set and $\phi$ a function, we write $\phi(S) := \{ \phi(x) : x \in S \}$.}.
\jessiet{Do we want the above statement? Meh}

@@

\begin{definition}
A property $\Gamma: \P \toto \R$ is \emph{finite} if $\R$ is finite. % $\im(\Gamma) := \{r\in\Gamma(p) : p\in\P, r \in \R \} = \bigcup_{p\in\P} \Gamma(p)$ is a finite set.
\end{definition}

@@

\begin{lemma}\label{lem:gam-prime-exists}
	Let $\Gamma:\P \toto \R$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$. 
\end{lemma}
\begin{proof}
	Construct the finite set $\R' = \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$, where $[r]$ is one consistent report for all the reports $r, r'$ such that $\Gamma_r = \Gamma_{r'}$. 
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	%Equivalently, we can observe for all $p \in \P$, that $\gamma(p) = \{ [r] : r \in \Gamma(p) \cap \R' \}$. %\jessie{Don't think this is necessary...?}
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.

	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$, so $[r] \in \gamma(p)$ and is well-defined for all $p \in \P$.
	Therefore, $\gamma$ is nondegenerate.

@@

	To see there are no reports $r, r'$ so that $\gamma_{r} \subsetneq \gamma_{r'}$, we use contradiction.
	Suppose there were such reports.
	By construction of $\R'$, we know both $\gamma_{r'}$ and $\gamma_r$ are full dimensional.
	\jessie{Here's where it gets hand-wavy}
	Therefore, we contradict convexity of the scoring rule $G$, since there is a bijection between the subgradients of $G$ and reports in $\R'$ (since we reduce to equivalent reports-- see Theorem~\ref{thm:bij-loss-to-score}).
	As $G$ is convex, it must be differentiable almost everywhere. 
	\jessiet{See Conjecture~\ref{conj:cvx-sets-nonempty-int-iff-pos-measure}}
	However, for every distribution in $\gamma_{r'} \cap \gamma_{r} = \gamma_{r'}$, the subgradient of $G$ is set-valued, and therefore $G$ is not differentiable on a set of positive Lebesgue measure in the simplex. 
	Contradicting the elicitability of $\gamma$, we conclude $\gamma$ is nonredundant.

@@

	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.
\end{proof}

@@

\begin{proof}
	Let $\gamma:\P \toto \bar\R$ and $\Gamma' : \P \toto \R'$ be nondegenerate, nonredundant properties so that $\gamma \preceq \Gamma$ and $\Gamma'\preceq \Gamma$.
	We want to show $\strip(\gamma) = \strip(\Gamma')$ in order to conclude that $\trim(\Gamma)$ is well-defined.
	For each $\bar r \in \bar\R$, there is a set of reports in $S \subseteq \R$ so that there is a full-dimensional level set $\theta = \bigcap_{s\in S}\Gamma_s$ and $\bar r = [s]$ for every $s \in S$.
	For the same set of reports $S$, we can equivalently choose a different representative report $r' \in \R'$ so that $r' = [s]$ for every $s \in S$, since $\Gamma' \preceq \Gamma$.

	There is then a bijection $\varphi : \bar \R \to \R'$ so that $\varphi(\gamma(p)) = \Gamma'(p)$ for all $p \in \P$.
	Thus, the level sets of each report are the same since they are restrictions of the same property, so $\strip(\gamma) = \{ \gamma_r : r \in \bar \R \} = \{ \Gamma_r : r \in \bar \R \} = \{ \Gamma_{\varphi(r)} : r \in \bar \R \} = \{ \Gamma_r : r \in \R' \} = \strip(\Gamma')$.
\end{proof}

%\begin{conjecture}\label{conj:trim-full-dim}
%	Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
%	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
%\end{conjecture}
%
%\begin{proof}
%	\jessie{Uses: Lemma~\ref{lem:gam-prime-exists}.}
%	
%	We define $\trim(\Gamma)$ in terms of the property $\gamma: \P \toto \R'$ such that $\gamma \preceq \Gamma$ and $\R'$ is as constructed in Lemma~\ref{lem:gam-prime-exists}.
%	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
%	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
%	Since $\theta$ has nonempty interior, then $\theta$ is full dimensional. 
%\end{proof}

\begin{lemma}\label{lem:lev-sets-subsets}
	Let the property $\Gamma: \P \toto \R$ be elicitable and the nondegenerate, nonredundant property $\gamma: \P \toto \R'$ so that $\gamma \preceq \Gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{lemma}

\begin{proof}
	It is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\gamma)$.
	Given $\theta \in \strip(\Gamma)$, there is some report $r \in \R$ so that $r \in \Gamma(p)$ for every $p \in \theta$.
	For every $r' \in \R'$, recall that there is an $r \in \R$ so that $r' = [r]$.
	By definition, $r \in \Gamma(p) \implies [r] = r' \in \gamma(p)$.
	Therefore, there is some $r' \in \R'$ so that $p \in \Gamma_r \implies p \in \Gamma_{[r]} = \gamma_{r'}$.
%	For every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ in two cases.
%	
%	First, if $r \not \in \R$, it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
%	In the second case, for $r \in \R$, we know $p \in \Gamma_{r} \implies p \in \{ p \in \P : r \in \Gamma(p) \cap \R \} = \{ p \in \P : r \in \gamma(p) \} = \gamma_{r}$. 
\end{proof}

@@

  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item $\strip(\Gamma)$ is finite. \jessie{Seems like we could just make note of this-- not sure if it needs its own statement.}
  \item $\trim(\Gamma)$ is finite. 
  \item $\trim(\Gamma)$ is finite and elicitable. \jessie{IMO, we can cut}
  \end{enumerate}
\end{proposition}

@@

\item[$4 \implies 1$] \jessiet{Cut}
Construct $\R' = \{ [r] \in \Gamma(p): p \in \inter{\theta} \}_{\theta\in\Theta}$ as in Lemma~\ref{lem:gam-prime-exists}.
Let $\varphi : \R' \to \reals^d$ be the identity and $\gamma := \Gamma|_{\R'}$.
Since $\trim(\Gamma)$ is finite, we then know $\R'$ is finite, and so $\gamma$ is a finite property.
We can then easily see that $r \in \gamma(r) \implies r \in \Gamma(p)$ as $\R' \subseteq \reals^d$.
Additionally, for any $r \in \R'$ so that $r \in \Gamma(p)$, we know that $r \in \Gamma|_{\R'} = \gamma$.
Therefore, $\Gamma$ embeds $\Gamma|_{\R'} = \gamma$.

%Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Lemma~\ref{lem:gam-prime-exists} to observe there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we show $\Gamma$ embeds $\gamma$.
%First, we know $\gamma$ is finite as there is only one report $r \in \R'$ per full dimensional level set, of which we know there are finitely many since $\trim(\Gamma)$ is finite (as each level set in $\trim$ is full dimensional from Conjecture~\ref{conj:trim-full-dim}).

@@

\item [$1 \implies 5$]
(Also shows $1 \implies 4$).

We know $\strip(\gamma) = \trim(\Gamma)$ \jessie{how...}, and as $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

\item [$5 \implies 2$]
(Also $4 \implies 2$)

Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$ by nondegneracy of $\Gamma$.

\item [$2 \implies 3$] \jessiet{Cut}
	We know there is a nonredundant, nondegenerate property $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Lemma~\ref{lem:gam-prime-exists} and the definition of trim (Lemma~\ref{lem:define-trim}).
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \Gamma_r = \gamma_r$ by Lemma~\ref{lem:lev-sets-subsets}, and we know that $\Gamma_{r'}$ has empty interior by the construction of $\R$ and nonredundancy of $\gamma$, as $\{p \in \P: \{r_1, r_2\} \in \gamma(p), [r_1] \neq [r_2] \}$ must have measure $0$ by the convexity of $G$.
	\jessie{Waving my hands at this again, but same argument as the proof of Conjecture 1.}

@@

\item [$3 \implies 4$]
\jessiet{Cut}
Since $\trim(\Gamma) \subseteq \strip(\Gamma)$, then the strip being finite implies the trim is finite.

\item[$2 \implies 1$]
\jessie{Only part needed if we decide to cut 3 and 5.}

Construct $\R' := \{[r] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
The property $\gamma: p \mapsto \Gamma(p) \cap\R'$ is then finite as $\R'$ is finite.
Taking $\varphi$ to be the identity, we observe $\Gamma$ embeds this finite $\gamma$.
\end{enumerate}

@@

%\begin{definition}\label{def:unlabeled-nonredundant}
%	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
%\end{definition}

@@

\begin{conjecture}\label{conj:cvx-sets-nonempty-int-iff-pos-measure}
A convex set is full-dimensional in $\reals^n$ iff it has positive Lebesgue mesaure.
\end{conjecture}
\begin{proof}

\begin{enumerate}
\item[$\implies$] A convex set that is full-dimensional contains the $\epsilon$-ball, which has positive measure. 
\item[$\impliedby$] A convex set of positive measure contains the ball, which is the superset of the convex hull of a $n$ affinely independent points, and therefore contains those points, so it is full dimensional by Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.
\end{enumerate}
\end{proof}
